From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-21 Pi+/paper/finite.tex
Text about prop-valued relation

\vc{Remark that $w \cox* v$ is not a proposition.}

>>>>

Note that this relation $\cox*$ is not $\hProp$-valued, that is, $w \cox* v$ is not a proposition because reductions are
not unique. Because of this, the quotient $\Sn$ is not effective, that is, $\quotrel : w \cox* v \to q(w) \id q(v)$ is
not an equivalence. We could truncate the relation to change this, but then the codomain of $\normf$ also needs to be
truncated. Instead, using the $\normf$ function, we could define a new relation
$(w \approx v) \defeq (\normf(w) \id \normf(v))$ which is $\hProp$-valued, and quotient $\List[\Fin[n]]$ by $\approx$.
This is not necessary because our results hold for $\cox*$ using the properties of the rewriting system we proved, and
we do not rely on the effectivity of the quotient.
